Urbanization and Public Transportation of Los Angeles

### 2023-11-27 Paper.Rmd
knit

---
title: "Urbanization and Public Transportation of Los Angeles"
author: "Kainoa Kanter, Julian Jacobson, Aidan Allen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    extra_dependencies: amsmath
  html_document:
    df_print: paged
abstract: This paper will examine how Los Angeles's demand for public transportation
  has been affected the last few years, utilizing derivatives to determine the rate
  of change in public transportation usage and studying the elasticity of demand for
  transportation options based on pricing, availability, convenience, and modes.
geometry: margin=1in
---

>>>>

---
title: "Urbanization and Public Transportation of Los Angeles"
author: "Kainoa Kanter, Julian Jacobson, Aidan Allen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document:
    extra_dependencies: amsmath
abstract: This paper will examine how Los Angeles's demand for public transportation
  has been affected the last few years, utilizing derivatives to determine the rate
  of change in public transportation usage and studying the elasticity of demand for
  transportation options based on pricing, availability, convenience, and modes.
geometry: margin=1in
---
